Effects of the body force on the evacuation dynamics

### 2019-12-29 paper.tex
Update paper.tex

The numerical setting of the parameters may affect the dynamics of the 
pedestrians. Some settings, however, yield similar collective dynamics. In 
order to investigate the similarities, we can introduce unit-less magnitudes 
and proceed straightforward as indicated in Appendix~\ref{appendix_1}. We 
realize from Appendix~\ref{appendix_1} that only three (unit-less) 
parameters  are the true ``control'' parameters for the collective dynamics. 
These are $\mathcal{A}$, $\mathcal{K}$, $\mathcal{K}_c$ as defined in 
Appendix~\ref{appendix_1}. Recall that $\mathcal{A}$ and $\mathcal{K}$ are 
precisely the same as in Ref.~\cite{dorso_2019}, but a novel $\mathcal{K}_c$ 
has been introduced due to the body force.   \\

@@

The set of parameters introduced within the context of the SFM (see 
Section~\ref{background}) affects the collective dynamics. The setting for 
these parameters may change...\\

>>>>

The numerical setting of the parameters may affect the dynamics of the 
pedestrians. Some settings, however, yield similar collective dynamics. In 
order to investigate these similarities, we can introduce unit-less magnitudes 
and proceed straightforward as indicated in \ref{appendix_1}. We realize from 
Appendix~\ref{appendix_1} that only three (unit-less) parameters  are the true 
``control'' parameters for the collective dynamics. These are $\mathcal{A}$, 
$\mathcal{K}$, $\mathcal{K}_c$ as defined in \ref{appendix_1}. Recall that 
$\mathcal{A}$ and $\mathcal{K}$ are precisely the same as in 
Ref.~\cite{dorso_2019}, but a novel $\mathcal{K}_c$ parameter has been 
introduced due to the body force.   \\

@@

An inspection of the diagrams in Fig.~\ref{venn_diagram} shows that the 
relaxation time (per unit mass) $\tau/m$ is always a common parameter, whether 
or not the body force is included in the model. \\
